A user-extensible and adaptable parser architecture

### 2008-05-23 papers/sgai-2008/paper.tex
Added some thoughts from Carl; it's now time to flesh everything out.

@@

\title*{A user-extensible and adaptable parser architecture}
%\author{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
%Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie \& vogel@cs.tcd.ie }
\author{John Tobin and Carl Vogel}
\institute{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie \& vogel@cs.tcd.ie }
\maketitle

@@

@@

Background of the project --- emphasise the variety in the log lines.
Motivation for creating the parser.  At some point I want to compare this
architecture to recursive decent parsers, Lex/Yacc parsers, XXX parsers.

@@

Split into framework, actions, \& rules.  Explain adding new rules and
actions.  Cut down rules to the minimum possible.  Framework provides
support functions, parsing loop, manages data --- boring stuff users don't
need to concern themselves with.

>>>>

\usepackage[acronym=true,style=altlist,number=none,toc=true]{glossary}
\makeglossary{}
\makeacronym{}

@@

\title*{A user-extensible and adaptable parser architecture}
%\author{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
%Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie \& vogel@cs.tcd.ie }
\author{John Tobin and Carl Vogel}
\institute{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ \email{tobinjt@cs.tcd.ie}
\email{vogel@cs.tcd.ie} }
\maketitle

@@

XXX FORMAT OF REFERENCES\@.

@@

Background of the project --- emphasise the variety in the log lines, and
the desire to achieve complete coverage, of both kinds.
Motivation for creating the parser.  At some point I MIGHT compare this
architecture to recursive decent parsers, Lex/Yacc parsers, XXX parsers.

@@

Split into framework, actions, \& rules.  Explain adding new rules and
actions.  Cut down rule attributes to the minimum possible.  Framework
provides support functions, parsing loop, manages data --- boring stuff
users don't need to concern themselves with.

Thoughts from Carl:

\begin{itemize}

    \item context-free rules

    \item partially context-aware actions, though not really

    \item transduction: input log lines $\rightarrow$ database

    \item Closer to NLP than fixed grammar.

\end{itemize}
